\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester in a particular Squad invested time to solve a problem, which was also faced by another tester on a different team. Without communication, members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
At Spotify, offices are laid out so that the Squads making up a Tribe are spatially close \cite{kniberg12}.
This leads to an environment where an informal exchange of information on the Tribe's work will occur.
%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

Consistency becomes an issue when expanding to multiple teams.
The product owner in an agile process model is the person with the project vision.
In a small team, they can clearly communicate it to every team member, and
members can even query the product owner.
However, in large projects with multiple teams, it is practically impossible for the owner to continue what they did in a small team.
This motivates a need for a formal definition of their vision as it gives teams something to consult to when encountering a design decision.
Without a functional specification, teams will be unable to produce components which can be easily integrated.

\section{Supporting Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at and across different levels need to have communication channels.
This can be addressed by adaptations in development process and leveraging technology.
Second, the quality (e.g., accuracy) of communication needs to be high.
This can be addressed by thorough system specification through architecture.

\subsection{Process Adaptations} 
\label{sec:proc_impv}
	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during development or integration.

%Changes in standups
One aspect of an agile process is daily standups which are a platform for letting each team member know the work being done by other team members. % and correlate it with their work.
This uncovers differences in understanding early and prevents last minute discovery of discrepancies.
For multiple teams, this problem is compounded as a stand up is a closed activity, preventing other teams from knowing the discussions of each other.
This can be resolved by having a representative from each team be present in a standup, e.g., a Scrum of Scrums, where stand up questions are given but reframed for a team \cite{Rubin12}.

%Changes to Product Owner
Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead in different directions.
This can be limited by regular meetings of product owners where the scope and vision of the project can be synchronized.


%Changes in Planning Sessions
All the initial, intermediate and final planning sessions should be organized such that teams which are, or could be, impacted by that part of the project are part of the meeting.
This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.

\subsection{Technology Improvements} \label{sec:tech_impv}
Selecting appropriate technology plays an important role in enabling communication and task management so that teams can work together efficiently.
%
%Communication Tools
Since agile focuses on interactions, like face-to-face conversation, conferencing tools can lower the bar to inter-team interactions.
They make communication real-time, reducing delay in communicating ideas across teams.
%Integration Tools
Continuous integration tools can go a long way in identifying inter-team problems early in development as it reveals the impact of changes on the entire project.


\subsection{Importance of Architecture and Design}\label{sec:imp_of_dsgn}
%Why is Design/Architecture so important when doing this?

System architecture acts as a common vision for not only the teams but also for communication between the product owners, and is the main topic for most of the inter-team communication that occurs in a multi-team environment.
%Being such a frequent piece of discussion
It needs to be as formal, and as clearly defined as possible, as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
%
A formal architecture description also helps to mitigate communication problems by reducing the need for inter-team communication as a good design document provides enough guidance for a developer to incorporate their work into the system.
Thus, a good design document sometimes acts as a proxy for a product owner when it comes to detailing the requirements of the customer.
%non specification fix
A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain a long term stewardship over a sub-system. 

Architecture can also be used to enable team agility.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach is ideal for agile development since it defines components in terms of hiding design decisions, which empowers teams to design their own solution.